Topological Sigma Models for Generalized Para-Complex Geometry

### 2020-01-17 old stuff/AKSZ.tex
old stuff folder

\documentclass[letterpaper,12pt]{article}
\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref,bm}
%-------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
\addtolength{\headwidth}{\marginparsep}
\addtolength{\headwidth}{\marginparwidth}
\addtolength{\headwidth}{0.25in}
%----------------
%\setlength{\marginparwidth}{0pt} % width of margin notes
%\setlength{\marginparsep}{0pt} % width of space between body text and margin notes
\setlength{\evensidemargin}{0.125in} % Adds 1/8 in. to binding side of all 
\setlength{\oddsidemargin}{0.125in} % Adds 1/8 in. to the left of all pages
\setlength{\textwidth}{6.375in} % assuming US letter paper (8.5 in. x 11 in.) and 
\raggedbottom
\setlength{\parskip}{\medskipamount}
\renewcommand{\baselinestretch}{1}
%---------------------------------
\newcommand{\TT}{{T\oplus T^*}}
\newcommand{\JJ}{\mathcal{J}}
\newcommand{\KK}{\mathcal{K}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Cc}{\mathbf{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\XX}{\mathfrak{X}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\FF}{\mathcal{F}}
\newcommand{\QQ}{\mathcal{Q}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\sA}{\mathcal{A}}
\newcommand{\cO}{\mathcal{O}}
\def\d{{\rm d}}
\def\dbar{\Bar{\partial}}
%----------------------------------------
\newcommand{\PP}{\mathrm{P}}
\newcommand{\PPt}{\tilde{\mathrm{P}}}
\newcommand{\id}{\mathbbm{1}}
\newcommand{\nlr}{\overset{\leftrightarrow}{\n}}
\newcommand{\lc}{\mathring{\n}}
\newcommand{\im}{\mathrm{Im}\,}
\newcommand{\Ker}{\mathrm{Ker}\,}
\newcommand{\Lie}{\mathcal{L}}
\newcommand{\PS}{\mathcal{P}}
\newcommand{\ap}{\alpha}
\newcommand{\bt}{\beta}
\def\w{\wedge}
\newcommand{\p}{\partial}
\newcommand{\pt}{\tilde{\partial}}
\newcommand{\xt}{{\tilde{x}}}
\newcommand{\n}{\nabla}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\PH}{(\PS,\eta,\omega)}
\newcommand{\Lt}{\tl{L}}
\newcommand{\Lb}{\mathbb{L}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\se}{\Gamma}
\newcommand{\Endo}{\text{End}}
\newcommand{\ellt}{{\tl{\ell}}}
\newcommand{\ot}{{1/2}}
\newcommand{\inv}{{-1}}
\newcommand{\Aa}{\mathcal{A}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\lara}{\la\ ,\ \ra}
\newcommand{\brac}{[\ ,\ ]}
\newcommand{\bl}{[\![}
\newcommand{\br}{]\!]}
\newcommand{\bracd}{\bl \ ,\ \br}
\newcommand{\yt}{\tl{y}}
\newcommand{\zt}{\tl{z}}
\newcommand{\tth}{\tl{\theta}}
\newcommand{\kk}{\mathrm{k}}
\newcommand{\Mt}{\tl{M}}
\newcommand{\pd}{\overline{\bm{\p}}}
\newcommand{\Mb}{\mathbb{M}}
\newcommand{\Drm}{\mathrm{D}}
\newcommand{\Dcal}{\mathcal{D}}
\newcommand{\wtl}{\widetilde}
%----------------------------------------
\def\gld{generalized Lie derivative }
\def\glds{generalized Lie derivatives }
\def\tl{\tilde}

@@

\maketitle
\begin{abstract}
We study a class of $2d$ topological sigma models that are formulated on generalized para-complex target manifolds via the AKSZ framework. When the target is additionally generalized para-K\"ahler, these topological theories can be realized as topological twists of $(2,2)$ para-supersymmetric sigma models of Abou-Zeid and Hull. We compare our results to the case of generalized complex and generalized K\"ahler geometry, where similar results have been described in the context of the usual $(2,2)$ SUSY by Kapustin and Li. We present several examples and show that our construction recovers the A-model and the Poisson sigma model as special cases. Moreover, we also introduce new examples of topological theories inherently tied to the para-complex geometry, the para-B-model and a para-complex version of the Landau-Ginzburg model.

\end{abstract}
\newpage
\tableofcontents
\newpage
\section{Introduction}

In \cite{HullTwistedSUSY}, Abou-Zeid and Hull studied the target geometry of certain $2D$ $(2,2)$ supersymmetric sigma models, which compared to the usual $(2,2)$ supersymmetry differ by a choice of sign in the supercommutator relations of its $4$ real supercharges:
\begin{align*}
\{Q_\pm,\tl{Q}_\pm\}=-2\p_\pm,
\end{align*}
with all other anti-brackets vanishing. The geometry of the target space of these sigma models reflects this sign change and in contrast to complex geometry needed for the usual supersymmetry, the target needs to be para-complex. More precisely, the required target geometry must be bi-para-Hermitian. In \cite{HullTwistedSUSY}, this type of supersymmetry was dubbed {twisted} SUSY, while the name {pseudo}-SUSY was used in various other works. Here we use the name {\bf para-SUSY} to reflect its relationship to para-complex geometry and to reserve the adjective ``twisted'' for the context of topological twists.

Para-complex structure on a manifold $\Mb$ is given by the data of an integrable endomorphism $K \in \End(T\Mb)$ such that $K^2=\id$ and its two eigenbundles corresponding to the $+1$ and $-1$ eigenvalues have the same rank. Consequently, $\Mb$ needs to have an even dimension $2n$. A para-Hermitian structure on $(\Mb,\eta)$ is then obtained by adding a compatible metric $\eta$:
\begin{align*}
\eta(K\cdot,K\cdot)=-\eta(\cdot,\cdot).
\end{align*}
This condition forces $\eta$ to be of signature $(n,n)$ and implies that $\omega=\eta K$ is an almost symplectic structure called the fundamental form of $K$. A bi-para-Hermitian geometry is then defined as a pair of para-Hermitian structures $(\eta,K_\pm)$ sharing the same metric and satisfying an additional condition
\begin{align}
\rd^p_\pm\omega_\pm=\pm H \in \Omega^3_{cl.}(\Mb),
\end{align}
where $\rd^p_\pm=K^*\circ \rd\circ K_\pm^*$ is the para-complex twisted differential and $\omega_\pm=\eta K_\pm$ are the fundamental forms of $K_\pm$.

In \cite{Hu:2019zro}, it is shown that the bi-para-Hermitian geometry $(\Mb,\eta,K_\pm,H)$ is equivalent to the data of a generalized para-K\"ahler geometry, which is defined as a pair of {\it generalized} para-complex (GpC) structures $\KK_\pm$ \cite{wade2004dirac,Zabzine:2006uz,Hu:2019zro} on $\Mb$,
\begin{align*}
\KK_\pm \in \End((\TT)\Mb), \quad \KK^2=\id, \quad \la \KK\cdot,\KK\cdot\ra=-\la\cdot,\cdot \ra,
\end{align*}
that commute and whose product $\GG=\KK_+\KK_-$ defines a split signature metric $G$ on $(\TT)\Mb$ via $G(\cdot,\cdot)=\la \GG\cdot,\cdot\ra$. Here, $\la\cdot,\cdot \ra$ is the symmetric duality pairing on $(\TT)M$ and the generalized para-complex endomorphisms $\KK_\pm$ satisfy a Courant integrability condition which ensures that its $\pm 1$-eigenbundles are Dirac structures \cite{courant1990dirac}.

Para-complex and para-Hermitian geometry was also recently studied as the description of the extended geometry in the context of T-duality \cite{freidel2017generalised,Freidel:2018tkj,Svoboda:2018rci,Marotta:2018myj}, following the earlier work of Vaisman \cite{vaisman2012geometry,vaisman2013towards}. In \cite{Marotta:2019eqc}, Szabo and Marotta described the bosonic sector of the $2D$ sigma models targeted in this extended geometry. Various topological models in the AKSZ framework on the para-Hermitian manifold $\Mb=T^*M\simeq M^n\times \RR^n$ were studied in \cite{Kokenyesi:2018xgj} and $3D$ membrane sigma models with this target were the subject of \cite{Chatzistavrakidis:2018ztm}. The generalized geometry corresponding to Para-Hermitian geometry and its refined version, Born geometry, has been studied in \cite{Hu:2019zro}.

\paragraph{Main results} In this paper, we combine the results of \cite{HullTwistedSUSY} and \cite{Hu:2019zro} to study the $2D$ topological sigma models with a generalized para-complex target manifold $(\Mb,\KK_+)$. This geometry leads to a $2D$ topological theory via the AKSZ formalism as follows. The Courant algebroid $(\TT)\Mb$ defines a $3D$ topological theory with a $2$-shifted symplectic NQ target space $({\cal E},\Omega)$ \cite{Roytenberg:2002nu}. Because the $\pm 1$-eigenbundles of $\KK$ are Dirac structures in $(\TT)\Mb$, they each define a Lagrangian in $({\cal E},\Omega)$, which are $1$-shifted symplectic NQ manifolds and as such define a $2D$ topological boundary theories.

Additionally, we show that when the GpC manifold $(\Mb,\KK_+)$ additionally admits a generalized para-K\"ahler structure $(\Mb,\KK_+,\KK_-)$, the topological theories for $(\Mb,\KK_+)$ described above can be realized as topological twists of the $(2,2)$ para-SUSY theory attached to $(\Mb,\KK_\pm)$.

We also present several explicit examples of our construction. The well-known examples include the Poisson sigma model of a real Poisson manifold $(\Mb,\Pi)$ that is described by the GpC structure
\begin{align*}
\KK_\Pi=
\begin{pmatrix}
\id & 2\Pi \\
0 & -\id
\end{pmatrix},
\end{align*}
the A-model of a symplectic manifold $(\Mb,\omega)$ described by the GpC structure
\begin{align*}
\KK_\omega=
\begin{pmatrix}
0 & \omega^{-1} \\
\omega & 0
\end{pmatrix},
\end{align*}
and also the BFF theory (?) that is simply given by the trivial GpC structure
\begin{align*}
\KK_0=
\begin{pmatrix}
\id & 0 \\
0 & -\id
\end{pmatrix}.
\end{align*}

The new examples that we describe are all tied to para-complex geometry. They are the para-complex version of the B-model of a para-complex manifold $(\Mb,K)$ that is given by the GpC structure
\begin{align*}
\KK_K=
\begin{pmatrix}
K & 0 \\
0 & -K^*
\end{pmatrix},
\end{align*}
and the para-complex topological Landau-Ginzburg model that can be seen as a deformation of the above geometry by a para-holomorphic poisson bi-vector $Q$
\begin{align*}
\KK_Q=
\begin{pmatrix}
K & Q \\
0 & -K^*
\end{pmatrix}.
\end{align*}

Importantly, our construction can also be applied to the more notoriously known generalized complex (GC) geometry, which was in the context of topological sigma models extensively studied in \cite{Zucchini:2004ta,Ikeda:2004cm,Kapustin:2004gv,Pestun:2006rj,Cattaneo:2009zx} to name some of the works, but to the authors' knowledge a similar construction to ours via a boundary reduction was not proposed before. Similarly in the GpC case, the GC structure defines a pair of Dirac structures (that are now tied by complex conjugation) and the $2D$ topological theory is recovered again as a boundary theory of the $3D$ theory defined by the underlying Courant algebroid. The advantage of our approach is that it provides a unified way to extract the data of a topological theory from any GC structure via a clear geometric procedure on the underlying shifted symplectic spaces. In the special case when the manifold is generalized K\"ahler \cite{Gualtieri:2003dx,Gualtieri:2010fd} -- implying it admits a $(2,2)$ SUSY --  the topological theories can again be realized as topological twists \cite{Kapustin:2004gv} of the $(2,2)$ theory. Here, the main examples are given by the A- and B- model corresponding to the GC structures $\JJ_\omega$ and $\JJ_I$, respectively:
\begin{align*}
\JJ_\omega=
\begin{pmatrix}
0 & -\omega^{-1} \\
\omega & 0
\end{pmatrix}, \quad
\JJ_I=
\begin{pmatrix}
I & 0 \\
0 & -I^*
\end{pmatrix},
\end{align*}
as well as the topological Landau-Ginzburg model which is again viewed via the deformation of $\JJ_I$ by a holomorphic poisson bi-vector \cite{Gualtieri:2007bq} $\sigma=-\frac{1}{4}(IQ+iQ)$:
\begin{align*}
\JJ_Q=
\begin{pmatrix}
I & Q \\
0 & -I^*
\end{pmatrix}.
\end{align*}

Notice, however, that for example the usual Poisson sigma model cannot be obtained in the realm of GC geometry because no GC structure is defined by a real Poisson structure $\Pi$.

%Since the work of (..) \cite{?} it has been known that on any K\"ahler manifold $(M,I,\omega)$, one can define a $2d$ sigma model admitting a $(2,2)$ supersymmetry (SUSY) and such model has a simple local description in terms of the K\"ahler potential.  Moreover, Witten has shown \cite{?} that such sigma model gives rise to two distinct topological theories -- the A- and B-models -- via a procedure called topological twisting. These topological theories have an important interpretation in terms of their underlying geometry: the A-model only depends on the symplectic structure $(M,\omega)$, while the B-model only depends on the complex structure $(M,I)$. Additionally, there exists an ${\mathbb Z}_2$ automorphism acting on the original $(2,2)$ supersymmetric theory that exchanges its A- and B-models. This is the simplest way one can observe the phenomenon of mirror symmetry in the context of $2d$ sigma models.
%
%The K\"ahler geometry does not describe the most general $(2,2)$ sigma model, as was shown in \cite{Gates-hull-rocek-biherm}. Instead, the most general geometry is described by a bi-Hermitian geometry, defined by a pair of complex structures $I_\pm$ compatible with the same Riemannian metric $g$ and satisfying the compatibility relation
%\begin{align*}
%\rd^c_\pm\omega_\pm=\pm H \in \Omega^3_{cl.}(M),
%\end{align*}
%$\omega_\pm$ being the fundamental forms of $I_\pm$ and $\rd^c_\pm$ the associated $\rd^c$-operators. For this geometry, the local description is more complicated than in the K\"ahler case, in particular because the analogue of the K\"ahler potential is much harder to describe. Consequently, the topological twists are also  more complicated.
%
%This problem is nevertheless partially mitigated by an alternative geometric formulation in terms of generalized K\"ahler (GK) geometry, which has been shown in \cite{Gualtieri:2003dx} to be equivalent to the above-described bi-Hermitian geometry $(g,I_\pm,H)$. A GK structure on $M$ is given by the data of two complex endomorphisms $\JJ_\pm$ of the bundle $(\TT)M$:
%\begin{align*}
%\JJ_\pm \in \End((\TT)M),\quad \JJ_\pm^2=-\id, \quad \la \JJ \cdot,\JJ\cdot \ra= \lara,
%\end{align*}
%where $\lara$ denotes the natural duality pairing on $(\TT)M$:
%\begin{align*}
%\la X+\ap,Y+\bt\ra=\ap(Y)+\bt(X),\quad X,Y\in \se(TM),\quad \ap,\bt \in \se(T^*M).
%\end{align*}
%Additionally, $\JJ_\pm$ are required to commute and their product $\GG\coloneqq -\JJ_+\JJ_-$ to define a

\subsection{Notations and conventions}

\brian{Conventions for odd Lie brackets $[-,-]$ and $\{-,-\}$.}

\section{Background on paracomplex and generalized geometry}
\david{would just put the introduction of paracomplex geometry (minus the generalized part) in appendix, we did that even in the other paper which is literally a differential geometry paper}

\subsection{Paracomplex geometry} \label{sec: paracomplex}

In this section we introduce para-complex geometry with emphasis on the analogy with complex geometry. More details can be found in \cite{Hu:2019zro} or \cite[Ch.~15]{Cortes:2010ykx}, for example. \brian{I think you should cite your work here too.}

\begin{Def}\label{def:paracpx}
An (almost) {\bf product structure} on a smooth manifold $\PS$ is an endomorphism $K\in \Endo(T\PS)$ which squares to the identity, $K^2=\id_{T\PS}$, $K\neq \id$. An (almost) \textbf{para-complex structure} is a product structure such that the $+1$ and $-1$ eigenbundles of $K$ have the same rank.
\end{Def}
A direct consequence of above definition is that any para-complex manifold is of even dimension. From now on, the $+1$ and $-1$ eigenbundles of an almost product/para-complex structure will be denoted $L$ and $\Lt$, respectively.

\paragraph{Integrability} The use of the word {\it almost} as usual refers to integrability of the endomorphism, i.e. whether its eigenbundles are involutive with respect to the Lie bracket and therefore define a foliation of the underlying manifold. Similarly to the complex case, the integrability is governed by the \textbf{Nijenhuis tensor}
\begin{align}\label{eq:nijenhuis}
\begin{aligned}
N_K(X,Y)&=[X,Y]+[KX,KY]-K([KX,Y]+[X,KY])\\
&=(\n_{KX}K)Y+(\n_XK)KY-(\n_{KY}K)X-(\n_YK)KX\\
&=4(\PP[\PPt X,\PPt Y]+\PPt[\PP X,\PP Y]),
\end{aligned}
\end{align}
where $\n$ is any torsionless connection and $\PP\coloneqq\frac{1}{2}(\id+K)$ and $\PPt\coloneqq\frac{1}{2}(\id-K)$ are the projections onto $L$ and $\Lt$, respectively. We say $K$ is integrable and call $K$ a product/para-complex manifold if $N_K=0$. From \eqref{eq:nijenhuis} it is apparent that $K$ is integrable if and only if {\it both} eigenbundles are simultaneously Frobenius integrable, i.e. involutive distributions in $T\PS$. This is one of the main differences between complex and para-complex geometry; one of the eigenbundles can be integrable while the other is not. In such cases, we call $\PS$ {\bf half-integrabile}. For more details, see for example \cite{??,??}.

\paragraph{Type decomposition} The splitting of the tangent bundle $T\PS=L\oplus \Lt$ gives rise to a decomposition of tensors analogous to the $(p,q)$-decomposition in complex geometry. For differential forms, we denote the decomposition as
\begin{align}\label{eq_plusminus_decomp}
\Lambda^k (T^*\mathcal{P})&=\bigoplus_{k=m+n}\Lambda^{(m,n)}(T^*\mathcal{P}),
\end{align}
where $\Lambda^{(m,n)}(T^*\mathcal{P})=\Lambda^m(T^{*}_{1,0})\otimes \Lambda^n(T^{*}_{0,1})$ and the corresponding sections are denoted by $\Omega^{(m,n)}(\mathcal{P})$. The bigradings \eqref{eq_plusminus_decomp} yield the natural projections
\begin{align*}
\Pi^{(p,q)}:\Lambda^k(T^*\mathcal{P})&\rightarrow \Lambda^{(p,q)}(T^*\mathcal{P}),
\end{align*}
so that when $K$ is integrable, the de-Rham differential splits as $\rd=\p+\tl{\p}$, where
\begin{align}\label{paracomplex_dels}
\begin{array}{cc}
\p \coloneqq \Pi^{(p+1,q)}\circ \rd, & \tl{\p} \coloneqq \Pi^{(p,q+1)}\circ \rd,
\end{array}
\end{align}
are the \textbf{para-complex Dolbeault operators}, satisfying
\begin{align*}
\p^2=\tl{\p}^2=\p\tl{\p}+\tl{\p}\p=0.
\end{align*}

One can also introduce the {\it twisted differential $\rd^p\coloneqq(\Lambda^{k+1}K^*)\circ\rd\circ (\Lambda^kK^*)$}. When $K$ is integrable, it can be simply written as $\rd^p=(\p_++\p_-)$ on real forms and $\rd^p=\kk (\p+\bar{\p})$ on para-complex forms.

\paragraph{Para-Holomorphic structure}

Let now $(\mathcal{P},K)$ be an almost para-complex manifold of dimension $2n$. If $K$ is integrable, we get a set of $2n$ coordinates $(x^i,\tilde{x}_i)$ called {\bf adapted coordinates}, $\mathcal{P}$ locally splits as $M\times \tilde{M}$, and $K$ acts as identity on $TM=L$ and negative identity on $T\tilde{M}=\tilde{L}$. The adapted coordinates therefore define two complimentary foliations that we will call {\bf canonical foliations} of the para-complex manifold $\PS$ and denote $M$ and $\Mt$. Both $M$ and $\Mt$ are therefore $n$-dimensional manifolds composed of connected components called leafs $M_i$, $\Mt_i$:
\begin{align*}
M=\bigcup_i M_i,\quad \Mt=\bigcup_i \Mt_i,
\end{align*}
and each are as sets equal to $\PS$.

As usual, a map of para-complex manifolds is called para-holomorphic if its pushforward commutes with the respective para-complex structures
\begin{Def}
Let $(M,K_M)$ and $(N,K_N)$ be para-complex manifolds. A map $F:M\rightarrow N$ is called para-holomorphic if
\begin{align}\label{eq:def_parahol}
K_N\circ F_*=F_*\circ K_M
\end{align}
\end{Def}
\begin{remark}
In the following we will omit the prefix ``para-'' in para-holomorphic whenever no confusion with complex holomorphicity is possible.
\end{remark}

Locally, the map $F:M\rightarrow N$ of para-complex manifolds can be understood via composition of coordinates as a
\begin{align*}
F&: \RR^{2n}\rightarrow \RR^{2m}\\
F=(f^i,\tl{f}_j)&=(y^i(x^k,\xt_l),\yt_j(x^k,\xt_l))^{i,j=1,\cdots,m}_{k,l=1,\cdots, n}, 
\end{align*}
where $(x^k,\xt_l)$ and $(y^i,\yt_j)$ are adapted local coordinates on $M$ and $N$, respectively. It is easy to check from \eqref{eq:def_parahol} that $F$ is a holomorphic map iff the components satisfy
\begin{align}\label{eq:holomorphic_real}
\frac{\p}{\p \xt_i}f^j=\frac{\p}{\p x^i}\tl{f}_j=0.
\end{align}

The conditions \eqref{eq:holomorphic_real} tell us that the holomorphic functions map the canonical foliations of the para-complex manifolds $M$ and $N$. This also means that the transition functions on a para-complex manifold (seen as maps $\RR^{2n}\rightarrow \RR^{2m}$) are holomorphic since the foliations must be preserved, i.e. the coordinates transform as
\begin{align}\label{para-coordinate-transf}
(x^i,\xt_i)\mapsto (y^j(x^i),\yt_j(\xt_i)).
\end{align}

This also gives us an intuition into what holomorphic bundles and their holomorphic sections look like. First, we notice that the tangent bundle $T\PS$ itself is a holomorphic bundle (see for example \cite{Cortes:2003zd,Hu:2019zro}); this is simply because of the form of the transition functions \eqref{para-coordinate-transf} that induce a holomorphic structure on the tangent bundle. The holomorphic sections of $T\PS$ -- the holomorphic vector fields -- are locally of the form
\begin{align*}
X= X^i(x)\p_i+\tl{X}_i(\xt)\pt^i,
\end{align*}
i.e. the components in $L$ and $\Lt$ individually define vector fields on the foliations $M$ and $\Mt$, respectively.

Similarly, the cotangent bundle is a holomorphic bundle. For the higher wedge powers, we find that only $\Lambda^{(k,0)+(0,k)}(T^*\PS)$, $1\leq k\leq n$, are holomorphic bundles. The {\bf para-complex Dolbeault complex} is therefore given by
\begin{align}\label{para-dolbeault}
\left(\Omega^{(\bullet,0)}\otimes\Omega^{(0,\bullet)},(\p,\pt)\right)\coloneqq \left(\mathbf{\Omega}^{0,\bullet},\pd\right).
\end{align}

\subsubsection{Para-Complexified Version}
In order to make the analogy between complex and para-complex geometry more explicit, one can \textit{paracomplexify} all objects by tensoring with the algebra $\mathbf{C}$ of \textbf{para-complex numbers}, which are given by ordered pairs $(x,y)\in \mathbb{R}\otimes (1,k)$ generated by $1$ and the symbol $k$, satisfying $k^2=1$ and called the para-complex unit. The elements $(x,y)\in \mathbf{C}$ can be therefore written as
\begin{align*}
\mathbf{C} \ni z=(x,y)=x+k\cdot y.
\end{align*}
On $\mathbf{C}$, we define following operations: para-complex conjugation $z=(x,y)\mapsto \bar{z}=(x,-y)$, i.e. $\overline{x+ky}=x-ky$, the real and imaginary parts given by $Re(z)=\frac{1}{2}(z+\bar{z})$, $Im(z)=k\frac{1}{2}(z-\bar{z})$, i.e. $Re(x+ky)=x,\ Im(x+ky)=y$.

Therefore, we see that $\mathbf{C}^n$ is a paracomplex vector space with the paracomplex structure given by the multiplication by $k$. Conversely, any $2n$-dimensional paracomplex vector space $(V,K)$ can be identified with $(\mathbf{C}^n,k)$; the $\mathbf{C}$-module structure is defined as $(a+kb)v=av+bK(v)$ and if $(x^i, \xt^i)$ is a basis of $V$ spanning the $\pm 1$ eigenspaces of $K$, then $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ is a basis of $\Cc^n$. In other words, we have the following identification of paracomplex vector spaces
\begin{align}\label{para-complexification}
\begin{aligned}
\begin{array}{ccc}
(\RR^n\times\RR^n,\id \times -\id) &\longleftrightarrow &(\Cc^n, k)\\
(x^i,\xt^i) &\mapsto &\frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i\\
(u^i+v^i,u^i-v^i) &\mapsfrom &u^i+kv^i,
\end{array}
\end{aligned}
\end{align}
where $i=1,\cdots,n$. If $(V,K)$ is a paracomplex vector space, then its paracomplexification, $V\otimes_\mathbb{R} \mathbf{C}\coloneqq V^\Cc$, splits to $\pm k$ eigenspaces of $K$, which is extended to $V^\Cc$ by linearity: $V^\Cc=V^{1,0}\oplus V^{0,1}$. The conjugation map is then an isomorphism between the two eigenspaces, i.e. $\overline{{V^{1,0}}}=V^{0,1}$. The splitting is given by the projections
\begin{align}
\PP^{1,0}=\frac{1}{2}(\id +kK),\quad \PP^{0,1}=\frac{1}{2}(\id -kK). \label{eq:projections_parac}
\end{align}

Let now $(\PS,K)$ be an almost paracomplex manifold. The para-complexified tangent bundle, $T\mathcal{P}^\mathbf{C}=T\mathcal{P}\otimes_\mathbb{R} \mathbf{C}$, splits to a $\pm k$ eigenbundles of $K$ as $T\mathcal{P}^\mathbf{C}=T\mathcal{P}^{1,0}\oplus T\mathcal{P}^{0,1}$. 
%and $T\mathcal{P}^{1,0}$ is isomorphic to $T\PS$ as real vector bundles:
%\begin{align*}
%\begin{aligned}
%\begin{array}{ccc}
%T\PS &\simeq &T\mathcal{P}^{1,0} \\
%X &\longmapsto &\frac{1}{2}(X+kKX) \\
%Re(X^{1,0})=\frac{1}{2}(X^{1,0}+\overline{X^{1,0}})&\longmapsfrom &X^{1,0}
%\end{array}
%\end{aligned}
%\end{align*}
Similarly to the real case, this induces a splitting of $\Lambda^k(T^*\mathcal{P}^\mathbf{C})$:
\begin{align*}
\Lambda^k(T^*\mathcal{P}^\mathbf{C})=\bigoplus_{k=p+q}\Lambda^{p,q}(T^*\mathcal{P}^\mathbf{C}),
\end{align*}
with the sections denoted as $\Omega^{p,q}_\mathbf{C}(\PS)$.
\begin{notation*}
To distinguish between the real and para-complexified bigradings, the former being with respect to the $\pm 1$ eigenvalues of $K$, while the latter is with respect to the $\pm k$ eigenvalues of $K$, we denote the real bigrading in round brackets, $(p,q)$, and the para-complexified grading without brackets, $p,q$.
\end{notation*}

The de-Rham differential also splits accordingly into the \textbf{para-complexified Dolbeault operators}
\begin{align*}
\p^\mathbf{C}&:\Omega^{p,q}_\mathbf{C}(\mathcal{P})\rightarrow \Omega_\mathbf{C}^{p+1,q}(\mathcal{P}),\\
\bar{\p}^\mathbf{C}&:\Omega_\mathbf{C}^{p,q}(\mathcal{P})\rightarrow \Omega_\mathbf{C}^{p,q+1}(\mathcal{P})\ .
\end{align*}

>>>>

\documentclass{article}
\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref}
%-------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
%----------------
\newcommand{\TT}{{T\oplus T^*}}
\newcommand{\JJ}{\mathcal{J}}
\newcommand{\KK}{\mathcal{K}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Cc}{\mathbf{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\XX}{\mathfrak{X}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\FF}{\mathcal{F}}
\newcommand{\QQ}{\mathcal{Q}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cO}{\mathcal{O}}
%----------------------------------------
\newcommand{\PP}{\mathrm{P}}
\newcommand{\PPt}{\tilde{\mathrm{P}}}
\newcommand{\id}{\mathbbm{1}}
\newcommand{\nlr}{\overset{\leftrightarrow}{\n}}
\newcommand{\lc}{\mathring{\n}}
\newcommand{\im}{\mathrm{Im}\,}
\newcommand{\Ker}{\mathrm{Ker}\,}
\newcommand{\Lie}{\mathcal{L}}
\newcommand{\PS}{\mathcal{P}}
\newcommand{\ap}{\alpha}
\newcommand{\bt}{\beta}
\def\w{\wedge}
\newcommand{\p}{\partial}
\newcommand{\pt}{\tilde{\partial}}
\newcommand{\xt}{{\tilde{x}}}
\newcommand{\n}{\nabla}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\PH}{(\PS,\eta,\omega)}
\newcommand{\Lt}{\tl{L}}
\newcommand{\Lb}{\mathbb{L}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\se}{\Gamma}
\newcommand{\Endo}{\text{End}}
\newcommand{\ellt}{{\tl{\ell}}}
\newcommand{\ot}{{1/2}}
\newcommand{\inv}{{-1}}
\newcommand{\Aa}{\mathcal{A}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\lara}{\la\ ,\ \ra}
\newcommand{\brac}{[\ ,\ ]}
\newcommand{\bl}{[\![}
\newcommand{\br}{]\!]}
\newcommand{\bracd}{\bl \ ,\ \br}
\newcommand{\yt}{\tl{y}}
\newcommand{\zt}{\tl{z}}
\newcommand{\tth}{\tl{\theta}}
\newcommand{\kk}{\mathrm{k}}
\newcommand{\Mt}{\tl{M}}
\newcommand{\pd}{\overline{\p\!\!\!\p}}
\newcommand{\Mb}{\mathbb{M}}
\newcommand{\Drm}{\mathrm{D}}
\newcommand{\Dcal}{\mathcal{D}}
\newcommand{\wtl}{\widetilde}

\def\sA{\mathcal{A}}
\def\d{{\rm d}}
\def\dbar{\Bar{\partial}}

%----------------------------------------
\def\gld{generalized Lie derivative }
\def\glds{generalized Lie derivatives }
\def\tl{\tilde}

@@

\section{The AKSZ formalism and para-geometry}
\def\fg{\mathfrak{g}}
In this section we will show how to associate a class of $2D$ topological field theories to generalized para-complex structures.
The construction closely follows the relationship between ordinary (non-para) generalized complex structures \cite{Gualtieri:2003dx} and $2D$ topological field theories developed in \cite{Cattaneo:2009zx, Pestun:2006rj}.
For another class of $2D$ boundary theories to the $3D$ Courant algebroid $\sigma$-model see \cite{SeveraTduality}. \btd{Please add any more references you think fit.}
